### 2022-09-28 main/chapter_searches.tex
fix quote linebreak; define SUSY in preface

\begin{singlespacing}
\chapter{Data analysis and \atlas\ searches}
\label{chapter:searches}
\begin{epigraphs}
\qitem{%
One way is to make it so simple that there are \emph{obviously} no deficiencies
\\
and the other way is to make it so complicated that there are no \emph{obvious}
deficiencies.%
}%
{Tony~Hoare,
\textit{The Emperor’s Old Clothes},
1981~\cite{hoare2007emperor}}
\end{epigraphs}
\end{singlespacing}
\noindent
Our aim in scientific data analysis is to distil useful messages from the
data, and to report that message to the wider community.
Various messages could be extracted from given data,
and those messages will have differing values to their recipients.
Data analysis is not an automatic process, but a design with many judgements
that are informed by theory, intuition, and convention to give value to their
results.

>>>>

\begin{singlespacing}
\chapter{Data analysis and \atlas\ searches}
\label{chapter:searches}
\begin{epigraphs}
\qitem{%
One way is to make it so simple that there are \emph{obviously} no deficiencies
and the\\
other way is to make it so complicated that there are no \emph{obvious}
deficiencies.%
}%
{Tony~Hoare,
\textit{The Emperor’s Old Clothes},
1981~\cite{hoare2007emperor}}
\end{epigraphs}
\end{singlespacing}
\noindent
Our aim in scientific data analysis is to distil useful messages from the
data, and to report that message to the wider community.
Various messages could be extracted from given data,
and those messages will have differing values to their recipients.
Data analysis is not an automatic process, but a design with many judgements
that are informed by theory, intuition, and convention to give value to their
results.

### 2022-09-28 main/frontmatter.tex
fix quote linebreak; define SUSY in preface

\TODO{Context of Standard Model theory, directions in which future developments
could improve it, and supersymmetric models}
Chapter~\ref{chapter:theory}

>>>>

\TODO{Context of Standard Model theory, directions in which future developments
could improve it, and supersymmetric models}
supersymmery (SUSY)
Chapter~\ref{chapter:theory}
